A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2019-01-09 doc/large_strain.tex
better stress novelty in conclusions

In this contribution, we proposed and numerically investigated several matrix-free implementations of tangent operators for finite-strain elasticity with heterogeneous materials.
The implementation that caches the material part of the fourth-order spatial tangent stiffness tensor together with the second-order Kirchhoff stress was shown to be faster than the matrix-based approach for quadratic elements in 3D and cubic {\color{red}elements} in 3D.
This gives hope that the matrix-free implementation of the tangent operator can be applied to any constitutive model which operates with the material part of the fourth-order spatial tangent stiffness tensor on the quadrature point level.

We also studied the performance of the GMG preconditioner with standard geometric transfer operations between each level.
The GMG was applied to heterogeneous material assuming that the coarsest level can provide an adequate discretization of the heterogeneity.
The numerical studies indicate that the proposed preconditioner leads to a solution approach that is faster than the matrix-based AMG for moderately high polynomial degrees (approximately up to order five).
However, a considerable amount of time of GMG preconditioner is spent in the coarse level solver.
Our future work will, therefore, be focused on extending the proposed matrix-free multigrid solution approach to homogenization based transfer operators \cite{Miehe2007}.
We are also interested in extending these methods to near incompressible three-field formulations.

>>>>

In this contribution, we proposed and numerically investigated {\color{red}three different} matrix-free implementations of tangent operators for finite-strain elasticity with heterogeneous materials.
{\color{red}
To the best of our knowledge, this is the first work that applies matrix-free sum factorization techniques to such materials.}
The implementation that caches the material part of the fourth-order spatial tangent stiffness tensor together with the second-order Kirchhoff stress was shown to be faster than the matrix-based approach for quadratic elements in 3D and cubic {\color{red}elements in 2D}.
{\color{red}
Given that in this case we did not utilize the specific form of the material part of the stiffness tensor, we conclude}
that the matrix-free implementation of the tangent operator can be applied to any constitutive model which operates with the material part of the fourth-order spatial tangent stiffness tensor on the quadrature point level.

{\color{red}
We also propose a method by which to construct level tangent operators and employ them to define a geometric multigrid preconditioner
}
with standard geometric transfer operations between each level.
The GMG was applied to heterogeneous material assuming that the coarsest level can provide an adequate discretization of the heterogeneity.
The numerical studies indicate that the proposed preconditioner is efficient from the perspective of linear algebra.
{\color{red}
Namely, the number of iterations in the iterative solver is almost independent on the polynomial degree of the finite element basis.
The multigrid matrix-free preconditioner also}
leads to a solution approach that is faster than the matrix-based AMG for moderately high polynomial degrees (approximately up to order five).
However, a considerable amount of time of GMG preconditioner is spent in the coarse level solver,
{\color{red}
which is the main bottleneck of the here considered iterative solver.}
Our future work will, therefore, be focused on extending the proposed matrix-free multigrid solution approach to homogenization based transfer operators \cite{Miehe2007}.
We are also interested in extending these methods to near incompressible three-field formulations.
